\documentclass[a4paper, 11pt]{article}

\usepackage{natbib}
\bibliographystyle{agsm}
\setcitestyle{authoryear,open={(},close={)}}

\input{layout.tex}

\title{\textbf{entrpreneur}\\tripadvisor open business}


\author{\textsc{Ans Vaessen}
\\13009722
\\{\textit{Entrepreneurship and Innovation}}}

\date{\today\\
word count: 3037}

%%%%%%%%%%%%%%%%% START %%%%%%%%%%%%%%%%%%

\begin{document}
\maketitle

\begin{abstract}
moet ik nog doen.
\end{abstract}



\vspace{30pt} % Some vertical space between the abstract and first section

\section*{Introduction}


With new business like tripadvisr and other open busines models the way of venture capitalist is changing and will  look into this using the agency theory


\section{Theory and funding}


Small and medium entrpreneurs will often need outside equity after the first initial face if they want to grow into a more mature company. This can take the form of venture capital investment, using the defintion by \citep{casson2008oxford} in the Oxford Handbook of Entrepreneurs.

\begin{quote}
"Venture capital investment consists in the purchase of shares of young, privatley held companies by outsiders for the primary purpose of capital gain" \citep[P.1]{casson2008oxford}.
\end{quote} 

However this capital injection brings some complications regarding the control of the company and the asymetry in information which are explained in the agency theory.


\subsection{Agency Theory}



In most companies that made use of outside equity there is a separation between the owner of the business (agent) and the lender or investor this can be a bank, venture capitalist or angel investor (principal). The principal wants security in return of the investment to ensure the money invested is used well and the principal is not harmed by actions of the agent \citep{jensen1976theory}.




There are asymmetries of information between the agent and the principal. The agent has information about the firm and its day to day operations that is not availble to the principle, and can harm the principal if the agents uses the information to benefit him or herself over the benefits of the principal \citep{Osnabrugge2000}.\cite{{Osnabrugge2000} continues to mention it is not easy for the principal to verify the information and the two parties can have different views on how to run the company best, so they set up contracts to limit the agency costs.


\subsection{Venture Capital}



\citep {casson2008oxford}.






\section{open business}



\cite {chesbrough2007companies}

As \cite{colombo2016open} argues that the growing popularity of open innovation is not research enough most models apply on closed business models. Open busines models (OBS) are businesses that use external sources of technology and knowledge or sharing their own knowledge with others. 


\subsection {tripadvisor}

\subsection {vc open busines}


\section{Conclusion}

And to conclude one could say bla bla bla


%% disable some things
\renewcommand{\textbf}{}
\renewcommand{\bf}{}
\bibliography{biblio}{}
\end{document}
